---
title: "Tutorial"
output: html_document
date: "2023-11-08"
vignette: > 
  %\VignetteIndexEntry{combcaculator Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(combcaculator)
```

This package is designed to make it quick and easy to compute the possible combination when selecting sample items. You can read more about combination at https://en.wikipedia.org/wiki/Combination.

To use the function "combination_count", you need to input the total number of elements N, and number of elements to select n.
As a specific example, one can compute the number of five-card hands possible from a standard fifty-two card deck as. In this case, N is 52, and n is 5.
```{r}
# N and n must be whole numbers
combination_count(52, 5)
```

To compare correctness against the original R function "combn()". 
"combn()" returns all possible combination, each as a column. In order to obtain the count, we take ncol(combn())
```{r}
all.equal(combination_count(52, 5), ncol(combn(52, 5)))
all.equal(combination_count(5, 1), ncol(combn(5, 1)))
all.equal(combination_count(3, 0), ncol(combn(3, 0)))
```
To compare the efficiency against the original R function "combn()". 
The current function is more efficient than the R basic fucntion for calculating the combination.
```{r, warning=F}
library(bench)
bench::mark(combination_count(52, 5), col(combn(52, 5)), check=F)
```

